
\documentclass[paper=a4,fontsize=11.5pt]{scrartcl}
					
\usepackage[pdftex]{graphicx}							
\usepackage[svgnames]{xcolor}							
\usepackage{geometry}
	\textheight=700px									
\usepackage{url}										
\usepackage{wrapfig}									
\pagestyle{empty}							
\usepackage{sectsty}						
\usepackage[colorlinks,linkcolor=green]{hyperref}

\sectionfont{\usefont{OT1}{phv}{b}{n}
	\sectionrule{0pt}{0pt}{-4pt}{2pt}}

\newlength{\spacebox}
\settowidth{\spacebox}{8888888888}			
\newcommand{\sepspace}{\vspace*{1em}}			

\newcommand{\MyName}[1]{
	\Huge\usefont{OT1}{phv}{b}{n} 
	\hfill #1 \par \normalsize \normalfont}
		
\newcommand{\MySlogan}[1]{
	\large\usefont{OT1}{phv}{m}{n}
	\hfill\textit{#1} 
	\par\normalsize\normalfont}

\newcommand{\NewPart}[1]{\section*{\uppercase{#1}}}

\newcommand{\PersonalEntry}[2]{
	\noindent\hangindent=2em\hangafter=0
	\parbox{\spacebox}{\textit{#1}}\hspace{1.5em} #2 \par}					

\newcommand{\SkillsEntry}[2]{
	\noindent\hangindent=2em\hangafter=0
	\parbox{\spacebox}{\textit{#1}}\hspace{1.5em} #2 \par}				
		
\newcommand{\EducationEntry}[4]{
	\noindent \textbf{#1} 
	\hfill\colorbox{White}{
		\parbox{6em}{\hfill\color{Black}#2}}
	\par\noindent\textit{#3}
	\par\noindent\hangindent=2em\hangafter=0 
	\small #4\normalsize \par}

\newcommand{\WorkEntry}[4]{	
		\noindent \textbf{#1} \hfill 					
		\colorbox{Black}{\color{White}#2} \par	
		\noindent \textit{#3} \par				
		\noindent\hangindent=2em\hangafter=0 \small #4 	
		\normalsize \par}

\begin{document}


\MyName{Yi Huang}
\MySlogan{Never say die!}

\sepspace


\NewPart{Personal details}{}

\PersonalEntry{Birth}{September 17, 1991} 
\PersonalEntry{Address}{
	255 Statenlaan, Tilburg, Netherlands}
\PersonalEntry{Phone}{(0316) 87134080}
\PersonalEntry{Mail}{\url{
		y.huang_4@tilburguniversity.edu}}


\NewPart{Education}{} 

\EducationEntry{Msc. Economics }{2015-till now}{Tilburg University, Netherlands}{Banking, money and financial markets}
\sepspace

\EducationEntry{Bsc. Economics}{2010-2014}{Guangxi University of Finance and Economics, China}{Top 1 student of general academic achievement; National Scholarship winner in 2013; honor graduate; Merit Student of Guangxi Province, China.}


\NewPart{Social experience}{}

\EducationEntry{Financial Manager}{2015.2-2015.6}{Shengfeng Micro-finance inc., Fuzhou, China, Internship}{Achieving mortgage finance target and reaching 2600 million RMB loan. }
\sepspace

\EducationEntry{Credit Administrator}{2014.2-2012.6}{Xiamen International Bank, Internship}{Helping creditors acquire loans and managing credit portfolios. Ensuring the accurate and efficient preparation of mortgage related documentation, including valuations, registration.}\sepspace

\EducationEntry{Co-founder}{2012.8-2015.6}{Eternal Spring, NGO., Germany}{First non-profit organization that accepts legal tender and bitcoins of China. The first social group in China that based block chain technology.}\sepspace

\EducationEntry{Administrative Assistant}{2012.7-2012.8}{Qinzhou Jinghui Real Estate inc.,China, Internship}{Participating in the administration of the General Manager’s office. Preparing and organizing materials for events and conference.Recording and reminding the general manager of his daily schedule.}
\sepspace

\EducationEntry{Volunteer}{2012.7-2012.8}{The 9th China - East Asia alliance exposition}{Collecting and managing business database.}
\sepspace

\NewPart{Skills}{}

\SkillsEntry{Languages}{Dutch (mother tongue)}
\SkillsEntry{}{English (fluent)}
\SkillsEntry{}{German (fluent)} \sepspace

\SkillsEntry{Software}{\textsc{Matlab}, \LaTeX, \textsc{Ansys}, \textsc{Comsol}}\sepspace

\SkillsEntry{Pro. Cert.}{Advanced Foreign Secretary Certificate, China}

\SkillsEntry{}{Human Resource Management Certificate (Grade 3), China}

\NewPart{Other Achievements}{}

\EducationEntry{National English Contest for College Students}{2012.6}{Winner's Prize}{College English Teaching Research Association Committee, China}
\sepspace
\EducationEntry{Debate Match in The Lotus Lake Economic Forum}{2011.4}{Third place}{Guangxi University of Finance and Economics, China}
\sepspace
\EducationEntry{National Challenge Cup Competition(Academic research)}{2011.1}{Second Prize}{Young people League of Guangxi, Education Bureau of Guangxi ,Technology Bureau of Guangxi, Guangxi Technology Association, Guangxi Students Union}
\sepspace
\NewPart{References}
Available upon request
\NewPart{Superlink}
\href{http://littleskyline.github.io/second-repo/NoCss.html}{Assignment 2: Presentation}//
\href{https://github.com/littleskyline/third-repo/blob/gh-pages/Numerical-Assignment.ipynb}{Assignment 3: Python}

\end{document}